---
title: "Using MOH DashBoard"
authors: "Or Duek & Guy Hazan"
output:
  html_document:
    toc: yes
    toc_depth: 5
    toc_float: yes
---


Load libraries
```{r}
library(tidyverse)
library(ggplot2)
library(survey)
library(survival)
library(survminer)

```

Loading data
```{r}
mohDat <- read.csv('MOH_data.csv')
n <- 10 # multiply the 100k. If 10 then 1M
newVacc <- mohDat$Number.of.new.vaccines # number of new vaccinations
# now we change it to accomodate to 1M people and think about first dose
newVacc <- newVacc / 6 / 2
#plot(newVacc)
sickNotVacc <- round(mohDat$Positive.PCR.per.100K...not.vaccinated*n) # simulate million
sickVacc <- round(mohDat$Positive.PCR.per.100K...vaccinated*n)
sick1stDose <- sickNotVacc * 0.4 # add 60% for first dose 
plot(sickNotVacc, col='red')
points(sickVacc, col='blue')
points(sick1stDose, col='green')
```
# Stratify to population

```{r}
N <- n * 100000 * 5
id <- 1:N
# build proportion of ages
(dat <- data.frame(min=c(15, 25, 40, 60, 75, 65), max=c(24, 34, 44, 54, 64, 100), prop=c(0.15, 0.134, 0.12, 0.1, 0.085,0.01)))
set.seed(144)  # For reproducibility
rows <- sample(nrow(dat), N, replace=TRUE, prob=dat$prop)
table(rows)
age <- round(dat$min[rows] + runif(N) * (dat$max[rows] - dat$min[rows]))
hist(age)
summary(age)

# gender
gender <- sample(c(0,1), N, replace = TRUE, prob = c(0.51, 0.49))
table(gender)
vaccination <- sample(c(0,1,2), N, replace = TRUE, prob = c(0.1, 0.3, 0.6))
df <- tibble(id=id,age=age, gender=gender)
df$gender <- factor(df$gender)
# generate age groups (for future use)
df$ageGroup <- cut(df$age, breaks=c(14,25,40,60,75,101), labels=c('<25','25-40','41-60','61-75','>75'))


df$firstDose <- 0 # start with no first dose
df$daysTo1st <- 0 # set days to get first vaccination
```

## Add vaccination (1st dose) and days from 

```{r}
dfVac <- df
dfRows <- sample(rownames(dfVac), newVacc[1])
dfNew <- dfVac[dfRows,]
dfNew$firstDose = 1
dfNew$daysTo1st = 1
dfVac <- dfVac[-as.numeric(dfRows),]

for (i in 2:length(newVacc)) {
  # distribute vaccinations
 # print(i)
  dfRows <- sample(rownames(dfVac), newVacc[i], replace = FALSE)
  dfTemp <- dfVac[dfRows,]
  dfTemp$firstDose = 1
  dfTemp$daysTo1st = i
  dfNew <-  rbind(dfNew, dfTemp)
  dfVac <- dfVac[-as.numeric(dfRows),]
 
}

# combine the dataset together
dfVac <- rbind(dfVac, dfNew)
dfNew <- NULL # dlete dfNew to avoid confusions
```

```{r}
hist(dfVac$daysTo1st)
```


# Now take new sick and distribute through synthetic population
- Including gender and age risks as well as vaccination

```{r}
## generate proportional units per demographic variable
aUnit <- 15*2.13 #28*2.13 # every decade (age). Can calculate as n(a1+a2)/2
ageProp <- 0.065#1 / aUnit ## 0.0023
# gender has two
sexProp <- 0.6#1 / 1.69
vac1 <- 0.4 # if one week from 1st dose then 0.4 from non vaccinated


dfVac$sickDay <- 500 # set value
for (days in 1:300) { # sicknotvacc vector is NAs from 300 to 327
  print(days)

nSick <- sickNotVacc[days]

# now to find relevant people from each
# grab people by gender age from dataset
# check if sick - if yes, grab another
# if no - add sick and day
# set levels
levelsG <- levels(dfVac$gender)
levelsAge <- levels(dfVac$ageGroup)
for (i in seq_along(levelsAge)) {
  
  for (g in seq_along(levelsG))
    # subseting
    if (g==1) {
      # setting scale for gender
      gscale = 0.4
    } else {gscale = 0.6}
    # now get size for that specific subset
    size = round(nSick * ageProp*i * gscale)
    print('size of sick')
    print(size)
    dfSub <- subset(dfVac, dfVac$gender==levelsG[g] & dfVac$ageGroup==levelsAge[i] & dfVac$sickDay==500)
    print('number of rows in subset')
    print(nrow(dfSub))
    samp <- sample(rownames(dfSub), size, replace = FALSE)  
    dfSub[samp,]$sickDay = days # here its 1 because its the first day
    
    # now need to bring back to dfVac
    mask <- dfVac$id %in% dfSub[samp,]$id # create a mask
    dfVac[mask,]$sickDay=days # change values in the relevant dataframe
}

}
```

# Plot

```{r}
hist(dfVac$sickDay)
summary(dfVac$sickDay)
# remove all healthy
dfSick <- subset(dfVac, dfVac$sickDay<500)
hist(dfSick$sickDay)
```


## Talk with Hazan and ideas:
- Generate weights per age/gender/vaccination (1st dose for now)
- Multiply all to get specific population
- subset data to grab that population and then randomly assign
- combine all data later


