---
title: "Simulation"
authors: "Or Duek & Guy Hazan"
output:
  html_document:
    toc: yes
    toc_depth: 5
    toc_float: yes
---


Load libraries
```{r}
library(tidyverse)
library(ggplot2)
library(survey)
library(survival)
library(survminer)

```


```{r}
N = 1000000 # number of people
id <- 1:N
# build proportion of ages
(dat <- data.frame(min=c(15, 25, 35, 45, 55, 65), max=c(24, 34, 44, 54, 64, 100), prop=c(0.15, 0.134, 0.12, 0.1, 0.085,0.01)))
set.seed(144)  # For reproducibility
rows <- sample(nrow(dat), N, replace=TRUE, prob=dat$prop)
table(rows)
age <- round(dat$min[rows] + runif(N) * (dat$max[rows] - dat$min[rows]))
hist(age)
summary(age)

# gender
gender <- sample(c(0,1), N, replace = TRUE, prob = c(0.51, 0.49))
table(gender)

df <- tibble(id=id,age=age, gender=gender)

# generate age groups (for future use)
df$ageGroup <- cut(df$age, breaks=c(14,25,35,45,55,65,75,85,101), labels=c('<25','25-35','35-45','45-55','55-65','65-75','75-85','>85'))
```

Try something on my own

```{r}
# set r rate
r=1.12
x <- round(N - N/3) # number of subjects - remove half to keep enough way for the assignment
sick <- 0
sick_new <- c(10)
 
for (i in 1:50) {
  print(i)
  x_new = x - sick
  #beta = rbeta(1,1,20)
  if(x_new > sick_new[i]*r) {
  sick_new[i+1] <- sick_new[i] * r #rbinom(1, x_new, beta)
  # assign to people
  
  sick <- sick + sick_new[i+1]
  } else {
    print('no more')
  }
  
}
plot(sick_new)


```

# Divide Sick to demographics



## Generate proportion table

```{r}
ndf = round(N/5) # set number to sample from
# age has 8 groups
aUnit <- 28*2.13 # every decade (age)
ageProp <- 1 / aUnit ## 0.0023
# gender has two
sexProp <- 1 / 1.69
propT <- data.frame(ID=sample(ndf), Name=sample(ndf), 
    ageGroup=sample(c('<25','25-35','35-45','45-55','55-65','65-75','75-85','>85'), ndf, prob=c(ageProp, ageProp*2, ageProp*3, ageProp*4, ageProp*5, ageProp*6, ageProp*7, ageProp*8), replace=TRUE),
    gender=sample(c(1, 0), ndf, prob=c(sexProp, 1-sexProp), replace=TRUE))

ageSexInt <- interaction(propT$ageGroup, propT$gender)
props <- table(ageSexInt)/length(ageSexInt) # generate proportion table for sampling



```

## Generate data of sick

```{r}
# run first outside of loop to create dfNew
dfTest <- df
dfTest$days <- 101 # set number of days higher then we want
dNum <- sick_new[1] # numbe
nstrat <- as.vector(round(dNum*props))
names(nstrat) <- names(props)
nstrat[nstrat==0] <- 1 # need to solve - for now to avoid zeores
dfRows <- stratsample(interaction(df$ageGroup, df$gender), nstrat)
dfNew <-  dfTest[dfRows,]
dfNew$days = 1
dfTest <- dfTest[-dfRows,]

for (j in 2:40) {
  dNum <- sick_new[j] # numbe
 # print(j)
  nstrat <- as.vector(round(dNum*props))
  names(nstrat) <- names(props)
  nstrat[nstrat==0] <- 1 
  dfRows <- stratsample(interaction(dfTest$ageGroup, dfTest$gender), nstrat)
  dfTemp <- dfTest[dfRows,]
  dfTemp$days = j
  dfNew <-  rbind(dfNew, dfTemp)
  
  dfTest <- dfTest[-dfRows,]

}

# add to original data
dfBoth <- rbind(dfNew, dfTest) # add entire population
```

## Look at the data

```{r}
nrow(subset(dfNew,gender==1)) / nrow(subset(dfNew,gender==0)) # ratio if 1.686 as expected
hist(dfNew$days)
ggplot(dfNew, aes(x=days)) + geom_histogram() + facet_grid(~ageGroup) + theme_minimal()
```



# Cox-Hazard

```{r}
# create a censor variable
# create a censore variable who survived more than 30 days
dfBoth$month <- case_when(dfBoth$days <= 30 ~ 1, TRUE ~ 0) # currently for 30 days survival
dfBoth$ageGroup <- relevel(dfBoth$ageGroup, ref='>85')
dfBoth$gender <- factor(dfBoth$gender, levels=c(0,1))
surv <- Surv(time = dfBoth$days, event = dfBoth$month)  
summary(surv)

# now cox analysis
fit.cox <- coxph(surv ~ ageGroup + gender, 
                   data = dfBoth)
ggforest(fit.cox, data = dfBoth)
```

# Discussion with Hazan
- Add vector of R from 1 to 1.5 to 0.8
- Add vaccination vector from real data
- Add vaccination effect (60% week after 1st dose and 92% week after 2nd dose)
- Try to test susceptibility after infection. 
- Also can use vector from Dashboard - then add a third column of 1st vaccination (60% from week 2-4)
